---
title: "Data preparation"
output:
  pdf_document: default
---

# Instructions

- You only need to submit the .Rmd of this file, not a PDF.

- You should __comment__ your code clearly to show what you've done to prepare the data.

- The purpose of this file is to use the data in the `data-raw` folder to create the data you will use in the report. The data you will use in the report should be saved in the `data` folder. It is good professional practice to make sure you're never directly modifying your raw data, but instead creating new datasets based on merges/manipulations that you need to reuse.

- Make sure you've taken a look at the hints for the web scraping and census API. 

- You may find the `write_rds()` function from the `readr` package helpful (it is loaded as part of the `tidyverse`).

- You do not need to keep the structure below.

# Set up

```{r, libraries}
# Set up any libraries you need
library(tidyverse)
library(haven)
library(rio)
library(readr)
library(plotly)
library(polite)
library(rvest)
library(cancensus)
```

# Loading client data

```{r}
break_glass <- read_rds("data-raw/break_glass_in_case_of_emergency.Rds")
cust_dev <- read_rds("data-raw/cust_dev.Rds")
cust_sleep <- read_rds("data-raw/cust_sleep.Rds")
customer <- read_rds("data-raw/customer.Rds")
device <- read_rds("data-raw/device.Rds")
```

# Getting external data

## Web scraping industry data

```{r}


url <- "https://fitnesstrackerinfohub.netlify.app/"

# Make sure this code is updated appropriately to provide 
# informative user_agent details
target <- bow(url,
              user_agent = "charlesjiahong.lu@utoronto.ca for STA303/1002 project",
              force = TRUE)

# Any details provided in the robots text on crawl delays and 
# which agents are allowed to scrape
target

html <- scrape(target)

device_data <- html %>% 
  html_elements("table") %>% 
  html_table() %>% 
  pluck(1) # added, in case you're getting a list format

device_data
```

## Postal Code data
```{r}

dataset = read_sav("data-raw/pccfNat_fccpNat_082021sav.sav")

postcode <- dataset %>% 
  select(PC, CSDuid) %>% 
  rename(c("postcode" = "PC"))
postcode %>% head()


```
# Census API

```{r}

options(cancensus.api_key = "CensusMapper_634a3db5365fd4910ad140001c90f3ee",
        cancensus.cache_path = "cache") # this sets a folder for your cache


# get all regions as at the 2016 Census (2020 not up yet)
regions <- list_census_regions(dataset = "CA16")

regions_filtered <-  regions %>% 
  filter(level == "CSD") %>% # Figure out what CSD means in Census data
  as_census_region_list()

# This can take a while
# We want to get household median income
census_data_csd <- get_census(dataset='CA16', regions = regions_filtered,
                          vectors=c("v_CA16_2397"), 
                          level='CSD', geo_format = "sf")

# Simplify to only needed variables
median_income <- census_data_csd %>% 
  as_tibble() %>% 
  select(CSDuid = GeoUID, contains("median"), Population) %>% 
  mutate(CSDuid = parse_number(CSDuid)) %>% 
  rename(hhld_median_inc = 2)
```
# data processing

```{r}
postcode_median_income <- postcode %>%
  distinct_all() %>%
  left_join(median_income) %>% 
  arrange(postcode, desc(Population)) %>% 
  group_by(postcode) %>% 
  summarise(hhld_median_inc = mean(hhld_median_inc, na.rm = TRUE),
            Population = sum(Population, na.rm = TRUE),
            CSDuid = first(CSDuid)) %>% 
  ungroup()
postcode_median_income

cust_dev_data <- customer %>% 
  ungroup() %>% 
  left_join(cust_dev) %>% 
  left_join(device) %>% 
  left_join(rename(device_data, c("device_name" = "Device name", 
                                  "line" = "Line"))) %>% 
  left_join(postcode_median_income)
cust_dev_data
```



