---
title: "Report title"
subtitle: "Subtitle that indicates findings"
author: "Report prepared for MINGAR by Simplicity"
date: 2022-04-11
lang: "en"
output:
  pdf_document:
    template: report.tex
    toc: true
    toc_depth: 2
titlepage: true
titlepage-color: "6C3082"
titlepage-text-color: "FFFFFF"
titlepage-rule-color: "FFFFFF"
titlepage-rule-height: 2
---

```{r, message = FALSE, echo=FALSE}
library(tidyverse)
library(lme4)
library(rvest)
library(polite)
library(lmtest)
library(kableExtra)
library(broom)
library(broom.mixed)
theme_set(theme_classic())

# this should suppress all code and messages
#knitr::opts_chunk$set(include=FALSE)
```

_The cover page must be a single stand alone page and have:_

*	_A title and subtitle (that indicate your findings)_
* _"Report prepared for MINGAR by" your company name_
*	_Date (assessment submission date is fine)_


\newpage
# Executive summary

_Guidelines for the executive summary:_

* _No more than two pages_
* _Language is appropriate for a non-technical audience_
* _Bullet points are used where appropriate_
*	_A small number of key visualizations and/or tables are included_
*	_All research questions are addressed_


_The [module 4 writing prompt](https://sta303-bolton.github.io/sta303-w22-courseguide/knowledge-basket-writing-and-peer-feedback.html#module-4-writing-task) provides some tips and information about writing executive summaries._


\newpage
# Technical report


## Introduction

In this report, Simplicity will tackle Mingar's most pressing questions to date, 
i.e. who are Mingar's customers of their newer and more cost-efficient wearable 
lines? And do the currently trending damaging claims of "racist" Mingar 
wearables hold any weight? Read on to find out.

Our company has gone through the exhaustive work of selecting the 2 best fitting 
models of the data that best answer each question by considering any predictors
that may influence our variable of interest, within the realm of common sense 
and reason backed by statistical tests, handy plots and colourful illustrations. 
Due to racial and ethnic privacy issues that prevent Mingar from collecting such 
data, we have rolled up our sleeves, wrangled the data and gotten creative with 
our approach to solving our client's questions. And in the spirit of 
transparency, we will explain any limitations that we ran into in the process.


### Research questions
Our report aims to address the 2 questions that Mingar has asked of us. More 
specifically, Question 1 targets primarily who Mingar's new customers of the 
affordable lines of wearables, "Active" and "Advance" are. We aim to highlight 
the specific significant factors that do and do not identify such customers.

Question 2 asks to find any device incompetencies found during sleep score flag 
records due to user skin color likely stemming from sensor quality issue or 
other data quality issue to determine whether there is racial bias existing 
within Mingar's wearables.


## Who are the "Active" and "Advance" Line Wearables Customers?

The data used for the purpose of this research question is based on the joint data of customer device, customer, and device data provided from the client Mingar. Then we further strengthen the data information by including living areas sorted by postal code, median income of areas, and population of the areas. Based on the existing variables, column age was created using Date of Birth information from the data. Column emoji color was also created based on the variable emoji modifier in the data. Users preferred emoji skin color can be used as an rough indicator of their skin color.


```{r, echo = FALSE}
dev_data <- read_rds("data/dev_data.Rds")
sleep_data <- read_rds("data/sleep_data.Rds")
```

```{r, echo = FALSE}
dev_data1 <- dev_data %>% 
  mutate(active_advance_user = if_else(active_advance_user==1, "active or advance user", "others user"))
```

```{r 1, echo = FALSE ,fig.cap="Density Distribution of Active or Advance Users vs. Other Device Users by Age", fig.width=8, fig.height=4}
  age_density <- dev_data1 %>% 
  ggplot(aes(x = age, fill = active_advance_user)) +
  labs(fill = "Type of Device uses")+ 
  geom_density(alpha = 0.2)

age_density
```


```{r 2,fig.cap="Density Distribution of Active or Advance Users vs. Other Device Users by Median Income", echo = FALSE,fig.width=8, fig.height=4}
median_inc_density <- dev_data1 %>% 
  ggplot(aes(x = hhld_median_inc, fill = active_advance_user)) + 
  labs(fill = "Type of Device uses")+ 
  geom_density(alpha = 0.2)

median_inc_density
```


```{r 3,fig.cap="Density Distribution of Active or Advance Users vs. Other Device Users by Post Code Population", echo = FALSE,fig.width=8, fig.height=4}
population_density <- dev_data1%>% 
  ggplot(aes(x = Population, fill = active_advance_user)) + 
  labs(fill = "Type of Device uses")+ 
  geom_density(alpha = 0.2)

population_density
```



```{r 4,fig.cap="Percent Distribution of Active or Advance Users vs. Other Device Users by Sex", echo = FALSE,message=FALSE,fig.width=8, fig.height=4}
dev_data1 %>% 
  mutate(sex = if_else(is.na(sex), "Unkown", sex)) %>% 
  group_by(active_advance_user, sex) %>% 
  summarise(N = n_distinct(cust_id)) %>% 
  ungroup() %>% 
  group_by(active_advance_user) %>% 
  mutate(total = sum(N)) %>% 
  ungroup() %>% 
  mutate(percent_label = N / total) %>% 
  ggplot(aes(x = active_advance_user, y = N, fill = sex)) + 
  geom_bar(stat = "identity") + 
  labs(x = "Type of Device uses", y = "Number of Users", fill = "Sex")+ 
  geom_text(aes(label = if_else(sex %in% c("Male", "Female"),paste(round(percent_label, 2) * 100, "%"),"")),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  )+coord_flip()
```


```{r 5,fig.cap="Density Distribution of Active or Advance Users vs. Other Device Users by Prefered Emoji Skin Tone", echo = FALSE,message=FALSE,fig.width=8, fig.height=4}
dev_data1 %>% 
  group_by(active_advance_user, emoji_color) %>% 
  summarise(N = n_distinct(cust_id)) %>% 
  ungroup() %>% 
  group_by(active_advance_user) %>% 
  mutate(total = sum(N)) %>% 
  ungroup() %>% 
  mutate(percent_label = N / total) %>% 
  ggplot(aes(x = active_advance_user, y = N, fill = emoji_color)) + 
  geom_bar(stat = "identity") + 
  labs(x = "Type of Device uses", y = "Number of Users", fill = "Emoji Skin Tone")+ 
  scale_fill_brewer()+
  geom_text(aes(label = paste(round(percent_label, 2) * 100, "%")),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  )+coord_flip()
```

To identify the target audiences for Mingar's new budget line up of devices Active and Advance, Simplicity decides to a binomial generalized linear model. The reason to select such model is due to the nature of the variable we are to study, active advance users. It consists of 1 and 0 where 1 represents user uses active or advance devices, and 0 otherwise. We want to determine the demographic backgrounds of active and advance users by using active advance users as outcome and various demographic background as the predictors. And a generalized linear model is a perfect fit for such task.
Through multiple nested likelihood ratio tests, testing on background variables like median income, age, sex, location, and potential skin colors,
The most appropriate model is given by:

$ActiveAdvanceUsers \sim Binomial(N,p)$ 

$log(\frac{p}{1-p})={\beta_0} +{\beta_1}MedianIncome+{\beta_2}Age+{\beta_3}Population$

Where $N$ represents the number of Device Users, and $p$ represents the probability of a device user uses Active or Advance given the information on median income and population. 


```{r, echo = FALSE}
dev_data=na.omit(dev_data)
#m1<- glm(active_advance_user~scales::rescale(hhld_median_inc),  data = dev_data, family = binomial)
m2<- glm(active_advance_user~scales::rescale(hhld_median_inc)+scales::rescale(age),  data = dev_data, family = binomial)
#m3<- glm(active_advance_user~scales::rescale(hhld_median_inc)+scales::rescale(age)+sex,  data = dev_data, family = binomial)
m4 <-glm(active_advance_user~scales::rescale(hhld_median_inc)+scales::rescale(age)+Population,  data = dev_data, family = binomial)
#m5 <-glm(active_advance_user~scales::rescale(hhld_median_inc)+scales::rescale(age)+Population + CSDuid,  data = dev_data, family = binomial)
#m6 <-glm(active_advance_user~scales::rescale(hhld_median_inc)+scales::rescale(age)+Population + emoji_color,  data = dev_data, family = binomial)
#lrtest(m1,m2)
#lrtest(m2,m3)
#lrtest(m2,m4)
#lrtest(m4,m5)
#lrtest(m4,m6)
kbl(broom::tidy(m4,exponentiate = TRUE,conf.int = TRUE, conf.type = "Wald")[,], caption = "Summary Table of The Generalized Linear Model", 
      digits = 3, format = "markdown", align = "ccccc", padding= 3)
```



For a generalized linear model to be valid, following assumptions needs to hold.

1. The model's response, the probability of Active Advance Users among the users should be independently distributed, and the errors are also assumed to be independent

2. The model assumes a linear relationship between the transformed response with the predictor variables. Which in this case is the $log(\frac{p}{1-p})$ and $age, median\ income,$ and $population$. Where $p$ represents the probability of a device user uses Active or Advance given the information on median income and population. 


```{r, fig.cap="Relationship of logit response and predictor values", echo = FALSE, message=FALSE}
a <- as.numeric(scales::rescale(dev_data$hhld_median_inc))
probabilities <- predict(m4, type = "response")
dev_data2 <- dev_data %>% mutate(stand_median_inc = (scales::rescale(dev_data$hhld_median_inc)),stand_age = (scales::rescale(dev_data$age)) )%>% select(hhld_median_inc, age, Population)
predictors <- colnames(dev_data2)
dev_data2 <- dev_data2 %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)
ggplot(dev_data2, aes(logit, predictor.value))+
  geom_point(size = 0.5, alpha = 0.5) +
  geom_smooth(method = "loess") + 
  theme_bw() + 
  facet_wrap(~predictors, scales = "free_y")
```
As seen from the figure, both age and median income have clear linear relationship with the transformed response, while population fails to reach the assumptions.

Although Population is significant predictor to the model, due to its low treatment effect on the probability of active or advance users, and its failure to reach the model assumptions. The predictor is removed from the model.

The new model is given by:

$ActiveAdvanceUsers \sim Binomial(N,p)$ 

$log(\frac{p}{1-p})={\beta_0} +{\beta_1}MedianIncome+{\beta_2}Age$

Where $N$ represents the number of Device Users, and $p$ represents the probability of a device user uses Active or Advance given the information on median income and population. 

```{r, echo = FALSE}
kbl(broom::tidy(m2,exponentiate = TRUE,conf.int = TRUE, conf.type = "Wald")[,], caption = "Summary Table of The Generalized Linear Model", 
      digits = 3, format = "markdown", align = "ccccc", padding= 3)
```



The model summary and confidence interval are almost identical to the previously proposed model, just without population as one of the model's predictor.


## Are Mingar Wearables Racist?


```{r 6,fig.cap="Relationship of average Sleep Duration and average Flags per User's Sleep", echo = FALSE,fig.width=8, fig.height=4}

duration_flag_byCust <- sleep_data %>% 
  group_by(cust_id) %>% 
  summarise(flags_mean = mean(flags, na.rm = T),
            duration_mean = mean(duration, na.rm = T)) %>% ungroup() 

duration_flag_byCust %>% 
  ggplot(aes(x = flags_mean, duration_mean)) + 
  geom_point()+
  labs(x = "average Flags", y = "average Sleep Duration")

```


```{r 7,fig.cap="Distribution of average Sleep Duration per User by preferred Emoji Skin Tone", echo = FALSE ,fig.width=8, fig.height=4, message=FALSE}
duration_color_byCust <- sleep_data %>% 
  group_by(cust_id) %>% 
  summarise(duration_mean = mean(duration, na.rm = T),emoji_color) %>% ungroup() 

duration_color_byCust %>% 
  ggplot(aes(x = emoji_color, duration_mean)) + 
  geom_boxplot(fill = "steel blue")+
  labs(x = "Emoji Skin Tone", y = "average Sleep Duration")
```


```{r 8, echo = FALSE ,fig.cap="Distribution of average Flags per User's sleep by preferred Emoji Skin Tone", fig.width=8, fig.height=4, message=FALSE}
flag_color_byCust <- sleep_data %>% 
  group_by(cust_id) %>% 
  summarise(flag_mean = mean(flags, na.rm = T),emoji_color) %>% ungroup() 

flag_color_byCust %>% 
  ggplot(aes(x = emoji_color, flag_mean)) + 
  geom_boxplot(fill = "steel blue")+
  labs(x = "Emoji Skin Tone", y = "average Flags")
```


```{r 9, echo = FALSE ,fig.cap="Relationship of average Sleep Duration and Age per User", fig.width=8, fig.height=4}
duration_age_byCust <- sleep_data %>% 
  group_by(cust_id) %>% 
  summarise(age_mean = mean(age, na.rm = T),
            duration_mean = mean(duration, na.rm = T)) %>% ungroup() 

duration_age_byCust %>% 
  ggplot(aes(x = age_mean, duration_mean)) + 
  geom_point()+
  labs(x = "Age", y = "average Sleep Duration")

```


```{r 10, echo = FALSE, fig.cap="Relationship of average Flags and Age per User's sleep", fig.width=8, fig.height=4, message=FALSE}
duration_age_byCust <- sleep_data %>% 
  group_by(cust_id) %>% 
  summarise(age_mean = mean(age, na.rm = T),
            flag_mean = mean(flags, na.rm = T)) %>% ungroup() 

duration_age_byCust %>% 
  ggplot(aes(x = age_mean, flag_mean)) + 
  geom_point()+
  labs(x = "Age", y = "average Flags")

```



```{r 11, fig.cap="Distribution of average flags per User's Sleep by Sex", echo = FALSE ,fig.width=8, fig.height=4, message=FALSE}
flag_sex_byCust <- sleep_data %>% 
  mutate(sex = if_else(is.na(sex), "unkown", sex))%>%
  group_by(cust_id) %>% 
  summarise(flag_mean = mean(flags, na.rm = T),sex) %>% ungroup() 

flag_sex_byCust %>% 
  ggplot(aes(x = sex, flag_mean)) + 
  geom_boxplot(fill = "steel blue")+
  labs(x = "Sex", y = "average Flags")
```


```{r 12, fig.cap="Relationship of average flags per User's Sleep and User's Postal Code Population", echo = FALSE ,fig.width=8, fig.height=4, message=FALSE}
flag_population_byCust <- sleep_data %>% 
  group_by(cust_id) %>% 
  summarise(flag_mean = mean(flags, na.rm = T), Population) %>% ungroup() 

flag_population_byCust %>% 
  ggplot(aes(x = Population, flag_mean)) +
  geom_point()+ geom_jitter()+
  labs(x = "Population", y = "average Flags")

```

Model2 is given by: 

$log(flags)= log(duration)+{\beta_1}emoji\_colorYellow+{\beta_2}emoji\_colorLight+{\beta_3}emoji\_colorMedium Light+ {\beta_4}emoji\_colorMedium+{\beta_5}emoji\_colorMedium Dark+{\beta_6}emoji\_colorDark+ U_i$ 

Where $U_i$ represents random effect for $Customer_i$. Because only dummy variables were used as predictors, the report decides not to use intercept for this model, and there will be no reference level. 

```{r, echo = FALSE}
#m1=glm(flags~emoji_color,offset=log(duration),family=poisson,data=sleep_data)
m2=glmer(flags~emoji_color+(1|cust_id),offset=log(duration),family=poisson,data=sleep_data)
#m3=glmer(flags~emoji_color+(1|cust_id) + (1|dev_id),offset=log(duration),family=poisson,data=sleep_data)
#m4=glmer(flags~emoji_color+scales::rescale(age)+(1|cust_id),offset=log(duration),family=poisson,data=sleep_data)
#m5=glmer(flags~emoji_color+scales::rescale(age)+ sex +(1|cust_id),offset=log(duration),family=poisson,data=sleep_data)
#m6=glmer(flags~emoji_color+scales::rescale(age) + scales::rescale(Population)+(1|cust_id),offset=log(duration),family=poisson,data=sleep_data)
#lrtest(m1,m2)
#lrtest(m2,m3)
#lrtest(m2,m4)
#lrtest(m2,m5)
#lrtest(m2,m6)
m2=glmer(flags~emoji_color+(1|cust_id)+0,offset=log(duration),family=poisson,data=sleep_data)
kbl(broom.mixed::tidy(m2,effects="fixed",exponentiate = TRUE,conf.int = TRUE, conf.type = "Wald")[,], caption = "Summary Table of The Poisson Generalized Linear Mixed Model", digits = 3, format = "markdown", align = "ccccc", padding= 3)

```




For a Poisson generalized linear mixed model to be valid, following assumptions needs to hold.

1. The model's response needs to be under Poisson distribution. Flags is a count variable that records the number of red flags over the period of user's sleep time, thus falls under Poisson distribution.

2. Random effect, which in this case are the customers should be normally distributed.

3. The customer's random effects errors and residual errors within preferred emoji skin should have constant variance.

4. The model assumes a that the transformed response must have a linear function with predictor variables. Which in this case is $log(Flags)$ and $emoji \\color$.

## Discussion

After selecting the most appropriate model for each question, we can now answer
the 2 questions at hand. 

Who Are the "Active" and "Advance" Line Wearables Customers? First, we have to
answer what the distinct characteristics of the "Active" and "Advance" 
customers are. Through the final selected generalized linear model, we see the 
most significant character traits to be income, age and number of residents in
the same neighbourhood. Furthermore, we see that there is a negative 
relationship between the active and advance customers binary response variable
and income, which reasons that wealthier individuals buy less of these 2 
lines, meanwhile lower income individuals buy more of them. In one of our plots
above, we see that customers less than 20 and over 60 buy more of the active 
and advance lines than the others. This suggests that once again adolescents or
young adults and seniors are more the target audience for these lines. This is 
congruent to our prior conclusions regarding income, i.e. individuals in those
age groups are generally regarded as having lower income looking for more 
affordable products. As for the last characteristic, population within a 
neighbourhood, conclusions are hard to draw as the relationship is unclear, 
though notably it is negative.

Are Mingar Wearables "Racist"? In short, yes. Let's talk about it...
Through our generalized linear mixed model, it was evident that the number of 
flags, which are quality issues that occur during sleep, related to sensor error 
or other data quality issues, increased for darker skin tones of overall the 
emoji modifiers; in exactly the order of Light, Medium Light, Medium, Medium 
Dark to Dark (least flags to most flags respectively). Moreover, out of the six 
models we considered, the most suitable model found the emoji modifier predictor 
to be the only significant one for the flag response variable, leaving us with 
the belief that the only consequential factor of these flags is the individual's 
skin tone. Our recommendation is that further tests on the hardware of the 
wearables should be conducted to determine the exact cause behind the skin tone 
sensitivity and lack of quality as a result.
### Strengths and limitations

Simplicity believes in transparency and as such, we find it important to 
disclose the limitations of our research and findings in order for our clients 
to feel confident with what they are receiving. Since we do not have information 
on individual income, we had to improvise. We cleverly pulled income information 
based on postal code from the postal code conversion file (2016 census 
geography, August 2021 postal codes) provided to us as University of Toronto 
students. Thus, we only have a general sense of the wealth of a customer based 
on the neighbourhood they live in. It may not be exactly accurate per consumer 
considering that high income individuals may reside in low income neighbourhoods 
and the opposite is true too; however we believe that our analysis provides 
insights as to the average buying behaviours of your wearables customers, 
important when answering you first set of questions.

Another limitation we encountered was discovered when tackling your second set 
of questions regarding the racial complaints against Mingar's devices. Since, as 
mentioned, Mingar does not collect any data on the racial ethnicity of its 
users, we had to get creative with identifying darker complexion customers from 
lighter ones. We utilized the emoji modifier field populated by the customer. We 
must warn that some users have no data within the emoji_modifier field (labeled 
as NA) as they have presumably not selected one, so we had to work within a 
subset of the customer data. Moreover, it is not exactly accurate to suggest 
that all customers use the same skin tone emoji modifier as their own, because 
people have complex skin tones and may find it difficult to select the right 
shade. Or they may simply slect the emoji that they wish to express themselves 
with regardless of their own shades. However, we believe, once again, that the 
average consumer will selected a fairly similar emoji modifier to their own skin 
colour; and that was how we were able to proceed with our analysis and provide 
some meaningful results.

Not to toot our own horn, but Simplicity prides itself on being expert model 
selectors, whereby we consider numerous models, six, in fact, per question. 
Through an open and diverse lens, we consider various predictors when answering 
both questions of focus to ensure we do not exclude any important factors. Our 
strong foundational understanding of distributions assisted us in deciding what 
the underlying distributions of the datasets that we cleverly were able to 
wrangle, join together and explore for the most meaningful models. Most 
importantly, our company's strong core beliefs of accountability and integrity
allows you to be assured that the final model selection was based on results 
that were authentic and reproducible with various illustrations, plots and tests 
to showcase the data and results.

\newpage
# Consultant information
## Consultant profiles

*Complete this section with a brief bio for each member of your group. If you are completing the project individually, you only need to complete one for yourself. In that case, change the title of this section to 'Consultant profile' instead. Examples below. This section is only marked for completeness, clarity and professionalism, not 'truth' so you can write it as if we're a few years in the future. Put your current degree in as completed and/or add your first choice grad school program, whatever you like. What skills related skills would you most like to highlight? What job title do you want?*

**Aaisha Eid**. Aaisha is a senior consultant at Google. She specializes in reproducible analysis and statistical communication. Aaisha earned her Bachelor of Science, Specialist in Statistics Machine Learning and Data Mining, from the University of Toronto in 2022.

**Charles Lu**. Charles is a junior consultant with Eminence Analytics. He specializes in data visualization. Charles earned their Bachelor of Science, Majoring in Computer Science and Statistics from the University of Toronto in 2024.

## Code of ethical conduct

Simplicity ensures that any information shared between itself and its clients remain confidential and protected against sale for personal gain or benefit. Conflicts of interest will surely be communicated to clients transparently and accordingly. Personal information provided to by clients will be treated anonymously and respectfully. Finally, Simplicity is operated by proud statisticians that uphold the professional statistical standards of procedure and analysis.

\newpage
# References

  R Core Team (2021). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria.
  URL https://www.R-project.org/.
  
  Douglas Bates, Martin Maechler, Ben Bolker, Steve Walker (2015). Fitting Linear Mixed-Effects Models Using lme4. Journal of Statistical
  Software, 67(1), 1-48. doi:10.18637/jss.v067.i01.

  Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686
  
  Achim Zeileis, Torsten Hothorn (2002). Diagnostic Checking in Regression Relationships. R News 2(3), 7-10. URL
  https://CRAN.R-project.org/doc/Rnews/
  
  Hao Zhu (2021). kableExtra: Construct Complex Table with 'kable' and Pipe Syntax. R package version 1.3.4.
  https://CRAN.R-project.org/package=kableExtra

  David Robinson, Alex Hayes and Simon Couch (2021). broom: Convert Statistical Objects into Tidy Tibbles. R package version 0.7.6.
  https://CRAN.R-project.org/package=broom

  Ben Bolker and David Robinson (2022). broom.mixed: Tidying Methods for Mixed Models. R package version 0.2.9.3.
  https://CRAN.R-project.org/package=broom.mixed

  Chung-hong Chan, Geoffrey CH Chan, Thomas J. Leeper, and Jason Becker (2021). rio: A Swiss-army knife for data file I/O. R package
  version 0.5.26.
  
  Hadley Wickham and Evan Miller (2020). haven: Import and Export 'SPSS', 'Stata' and 'SAS' Files. R package version 2.3.1.
  https://CRAN.R-project.org/package=haven
  
  Hadley Wickham and Jim Hester (2020). readr: Read Rectangular Text Data. R package version 1.4.0.
  https://CRAN.R-project.org/package=readr

  Hadley Wickham (2021). rvest: Easily Harvest (Scrape) Web Pages. R package version 1.0.2. https://CRAN.R-project.org/package=rvest

  von Bergmann, J., Dmitry Shkolnik, and Aaron Jacobs (2021). cancensus: R package to access, retrieve, and work with Canadian Census data
  and geography. v0.4.2.
  
  Unicode, Inc. (2022). Unicode character table. Retrieved April 11, 2022, from https://unicode-table.com/en/ 

  
\newpage
# Appendix

## Web scraping industry data on fitness tracker devices
The industry data on fitness tracker devices was web scrapped in R from https://fitnesstrackerinfohub.netlify.app/.
the whole web scraping process utilizes the R packages "polite" and "rvest".
informative user agents details including purpose of web scraping and contact information was provided to website before scraping.
It is important to note that to respect the web scrapped contents, follow the terms and services and Robots.txt of the website and only take what is needed.
Avoid web scraping at all if the target website provide public API to access the data.
Respect the crawl limit suggested by the website.
The web scraping industry data on fitness tracker devices are private data saved under the folder raw-data, and will never be shared and published on Github or any websites.

## Accessing Census data on median household income
The Canada Census data on median household income was accessed from https://censusmapper.ca/ through the APIs of R package "cancencus" and the private API key kindly provided by CensusMapper.
The data is governed by the Statistic Canada Open Data license and Statistic Canada, and acknowledgment of them is required use the data.
The Census data are licensed data saved under the folder raw-data, and will never be shared and published on Github or any websites.
The API key provided by CensusMapper should also not be shared anywhere as it is a personal private key.

## Accessing postcode conversion files
The postal code conversion files was downloaded from https://mdl.library.utoronto.ca/collections/numeric-data/census-canada/postal-code-conversion-file through using University of Toronto student credentials.
The file is governed by Statistic Canada and stored in University of Toronto online map and data library.
Same as the Census data, the file is classified as licensed data saved under the folder raw-data, and will never be shared and published on Github or any websites.

