---
title: "Report title"
subtitle: "Subtitle that indicates findings"
author: "Report prepared for MINGAR by [consulting company name]"
date: 2022-04-11
lang: "en"
output:
  pdf_document:
    template: report.tex
    toc: true
    toc_depth: 2
titlepage: true
titlepage-color: "6C3082"
titlepage-text-color: "FFFFFF"
titlepage-rule-color: "FFFFFF"
titlepage-rule-height: 2
---

```{r, message = FALSE, echo=FALSE}
library(tidyverse)
library(lme4)
library(rvest)
library(polite)
library(lmtest)
library(kableExtra)
library(broom)
theme_set(theme_classic())

# this should suppress all code and messages
knitr::opts_chunk$set(include=FALSE)
```

# General comments (you can delete this section)

_Before making any changes, knit this Rmd to PDF and change the name of the PDf to something like 'original-instructions.pdf', or whatever you like (it is just for your reference).. Then you can delete this section and if you want to check what it said, just open the other PDF. You don't HAVE to use this particular template, but you DO need to write you report in RMarkdown and include a cover page._

_The cover page must be a single stand alone page and have:_

*	_A title and subtitle (that indicate your findings)_
* _"Report prepared for MINGAR by" your company name_
*	_Date (assessment submission date is fine)_

_You can change the colour of this cover to any colour you would like by replacing 6C3082 in the YAML above (`titlepage-color:`) to another hex code. You could use this tool to help you:_ https://htmlcolorcodes.com/color-picker/

_Note: There should NOT be a table of contents on the cover page. It should look like a cover._

\newpage
# Executive summary

_Guidelines for the executive summary:_

* _No more than two pages_
* _Language is appropriate for a non-technical audience_
* _Bullet points are used where appropriate_
*	_A small number of key visualizations and/or tables are included_
*	_All research questions are addressed_


_The [module 4 writing prompt](https://sta303-bolton.github.io/sta303-w22-courseguide/knowledge-basket-writing-and-peer-feedback.html#module-4-writing-task) provides some tips and information about writing executive summaries._


\newpage
# Technical report
_This part of the report is much more comprehensive than the executive summary. The audience is statistics/data-minded people, but you should NOT include code or unformatted R output here._


## Introduction

In this report, Simplicity will tackle Mingar's most pressing questions to date, 
i.e. who are Mingar's customers of their newer and more cost-efficient wearable 
lines? And do the currently trending damaging claims of "racist" Mingar 
wearables hold any weight? Read on to find out.

Our company has gone through the exhaustive work of selecting the 2 best fitting 
models of the data that best answer each question by considering any predictors
that may influence our variable of interest, within the realm of common sense 
and reason backed by statistical tests, handy plots and colourful illustrations. 
Due to racial and ethnic privacy issues that prevent Mingar from collecting such 
data, we have rolled up our sleeves, wrangled the data and gotten creative with 
our approach to solving our client's questions. And in the spirit of 
transparency, we will explain any limitations that we ran into in the process.


### Research questions
Our report aims to address the 2 questions that Mingar has asked of us. More 
specifically, Question 1 targets primarily who Mingar's new customers of the 
affordable lines of wearables, "Active" and "Advance" are. We aim to highlight 
the specific significant factors that do and do not identify such customers.

Question 2 asks to find any device incompetencies found during sleep score flag 
records due to user skin colour likely stemming from sensor quality issue or 
other data quality issue to determine whether there is racial bias existing 
within Mingar's wearables.


## Who are the "Active" and "Advance" Line Wearables Customers?

_For each research question, you will want to briefly describe any data manipulation, show some exploratory plots/summary tables, report on any methods you use (i.e. models you fit) and the conclusions you draw from these_
```{r}
dev_data <- read_rds("data/dev_data.Rds")
sleep_data <- read_rds("data/sleep_data.Rds")
```

```{r}
dev_data=na.omit(dev_data)
m1<- glm(active_advance_user~scales::rescale(hhld_median_inc),  data = dev_data, family = binomial)
m2<- glm(active_advance_user~scales::rescale(hhld_median_inc)+scales::rescale(age),  data = dev_data, family = binomial)
m3<- glm(active_advance_user~scales::rescale(hhld_median_inc)+scales::rescale(age)+sex,  data = dev_data, family = binomial)
m4 <-glm(active_advance_user~scales::rescale(hhld_median_inc)+scales::rescale(age)+Population,  data = dev_data, family = binomial)
m5 <-glm(active_advance_user~scales::rescale(hhld_median_inc)+scales::rescale(age)+Population + CSDuid,  data = dev_data, family = binomial)
m6 <-glm(active_advance_user~scales::rescale(hhld_median_inc)+scales::rescale(age)+Population + emoji_color,  data = dev_data, family = binomial)
##kbl(broom::tidy(fit1)[,], caption = "Summary Table of Model1", digits = 3, format = "markdown", align = "ccccc", padding= 3) 
#lrtest(m1,m2)
#lrtest(m1,m3)
#lrtest(m3,m4)
#lrtest(m4,m5)
#lrtest(m4,m6)
summary(m4)
```


## Are Mingar Wearables Racist?
```{r}
sleep_data=na.omit(sleep_data)
m1=glm(flags~emoji_color,offset=log(duration),family=poisson,data=sleep_data)
m2=glmer(flags~emoji_color+(1|cust_id),offset=log(duration),family=poisson,data=sleep_data)
m3=glmer(flags~emoji_color+(1|cust_id) + (1|dev_id),offset=log(duration),family=poisson,data=sleep_data)
m4=glmer(flags~emoji_color+scales::rescale(age)+(1|cust_id),offset=log(duration),family=poisson,data=sleep_data)
m5=glmer(flags~emoji_color+scales::rescale(age)+ sex +(1|cust_id),offset=log(duration),family=poisson,data=sleep_data)
m6=glmer(flags~emoji_color+scales::rescale(age) + scales::rescale(Population)+(1|cust_id),offset=log(duration),family=poisson,data=sleep_data)
#lrtest(m1,m2)
#lrtest(m2,m3)
#lrtest(m2,m4)
#lrtest(m4,m5)
#lrtest(m4,m6)

summary(m4)
```

## Discussion

_In this section you will summarize your findings across all the research questions and discuss the strengths and limitations of your work. It doesn't have to be long, but keep in mind that often people will just skim the intro and the discussion of a document like this, so make sure it is useful as a semi-standalone section (doesn't have to be completely standalone like the executive summary)._

### Strengths and limitations

Simplicity believes in transparency and as such, we find it important to 
disclose the limitations of our research and findings in order for our clients 
to feel confident with what they are receiving. Since we do not have information 
on individual income, we had to improvise. We cleverly pulled income information 
based on postal code from the postal code conversion file (2016 census 
geography, August 2021 postal codes) provided to us as University of Toronto 
students. Thus, we only have a general sense of the wealth of a customer based 
on the neighbourhood they live in. It may not be exactly accurate per consumer 
considering that high income individuals may reside in low income neighbourhoods 
and the opposite is true too; however we believe that our analysis provides 
insights as to the average buying behaviours of your wearables customers, 
important when answering you first set of questions.

Another limitation we encountered was discovered when tackling your second set 
of questions regarding the racial complaints against Mingar's devices. Since, as 
mentioned, Mingar does not collect any data on the racial ethnicity of its 
users, we had to get creative with identifying darker complexion customers from 
lighter ones. We utilized the emoji modifier field populated by the customer. We 
must warn that some users have no data within the emoji_modifier field (labeled 
as NA) as they have presumably not selected one, so we had to work within a 
subset of the customer data. Moreover, it is not exactly accurate to suggest 
that all customers use the same skin tone emoji modifier as their own, because 
people have complex skin tones and may find it difficult to select the right 
shade. Or they may simply slect the emoji that they wish to express themselves 
with regardless of their own shades. However, we believe, once again, that the 
average consumer will selected a fairly similar emoji modifier to their own skin 
colour; and that was how we were able to proceed with our analysis and provide 
some meaningful results.

Not to toot our own horn, but Simplicity prides itself on being expert model 
selectors, whereby we consider numerous models, six, in fact, per question. 
Through an open and diverse lens, we consider various predictors when answering 
both questions of focus to ensure we do not exclude any important factors. Our 
strong foundational understanding of distributions assisted us in deciding what 
the underlying distributions of the datasets that we cleverly were able to 
wrangle, join together and explore for the most meaningful models. Most 
importantly, our company's strong core beliefs of accountability and integrity
allows you to be assured that the final model selection was based on results 
that were authentic and reproducible with various illustrations, plots and tests 
to showcase the data and results.

\newpage
# Consultant information
## Consultant profiles

*Complete this section with a brief bio for each member of your group. If you are completing the project individually, you only need to complete one for yourself. In that case, change the title of this section to 'Consultant profile' instead. Examples below. This section is only marked for completeness, clarity and professionalism, not 'truth' so you can write it as if we're a few years in the future. Put your current degree in as completed and/or add your first choice grad school program, whatever you like. What skills related skills would you most like to highlight? What job title do you want?*

**Aaisha Eid**. Aaisha is a senior consultant at Google. She specializes in reproducible analysis and statistical communication. Aaisha earned her Bachelor of Science, Specialist in Statistics Machine Learning and Data Mining, from the University of Toronto in 2022.

**Charles Lu**. Charles is a junior consultant with Eminence Analytics. He specializes in data visualization. Charles earned their Bachelor of Science, Majoring in Computer Science and Statistics from the University of Toronto in 2024.

## Code of ethical conduct

Simplicity ensures that any information shared between itself and its clients remain confidential and protected against sale for personal gain or benefit. Conflicts of interest will surely be communicated to clients transparently and accordingly. Personal information provided to by clients will be treated anonymously and respectfully. Finally, Simplicity is operated by proud statisticians that uphold the professional statistical standards of procedure and analysis.

\newpage
# References

_You don't need to cite course materials, but consider all the the places you got data from, as well as the packages used and R itself. These are all things you should consider citing. Likewise, you might use some external resources on the emoji skin tones/Fitzpatrick scale, etc._

\newpage
# Appendix

_These appendices should outline in more detail the steps taken to access the following datasets. They should NOT include code, but should briefly describe the steps and important considerations. I.e., show that you understand what needs to be considered when web scraping, protecting licensed data, etc._

## Web scraping industry data on fitness tracker devices

## Accessing Census data on median household income

## Accessing postcode conversion files


__Final advice: KNIT EARLY AND OFTEN!__
